---

title: "LST-R-Projection"
author: "Aji John"
date: "8/28/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the required

```{r}
library(sp)
library(dplyr)
```
## R Markdown

Get the latest imagery

```{r}
#link to the latest satellite imagery
latest <-'SUPER-NATIONAL_1km_SFC-T_20170828_2000.gini.nc'

```

## Including Plots

Open the gini as netCDF

```{r, echo=FALSE}
#read the GINI as netCDF file
# load the ncdf4 package
library(ncdf4)
# open a netCDF file
ncin <- nc_open(latest)
print(ncin)
```

get the surface temperature variable

```{r, echo=FALSE}

sfct <- ncvar_get(ncin, "SFC_T")
dim(sfct)

```

sfct is a two dimenional array

```{r, echo=FALSE}

x <- ncvar_get(ncin,"x")
nx <- dim(x)
head(nx)
summary(x)
```

```{r, echo=FALSE}
# get proj y
y <- ncvar_get(ncin,"y")
ny <- dim(y)
head(ny)
summary(y)
```

Time is only for onetimestamp
```{r, echo=FALSE}
print(c(nx,ny))
# get time
time <- ncvar_get(ncin,"time")
time

tunits <- ncatt_get(ncin,"time","units")
nt <- dim(time)
as.character(ncin$dim$time$vals)
```

Assuming that this timestamp is in milliseconds:
GMT: Friday, August 25, 2017 7:00:00 PM


Our goal is to create spatial points dataframe

```{r, echo=FALSE}
# get proj y
xy <- as.data.frame(expand.grid(x,y))
coordinates(xy)= ~Var1 + Var2
sfct_df <- data.frame(sfct = as.vector(sfct))
lst_sp_fw <- SpatialPointsDataFrame(coordinates(xy), data =sfct_df
                                    , proj4string = CRS("+ellps=sphere +a=6371200.0 +b=6371200.0 +proj=stere +lat_0=90 +lon_0=-105.0 +x_0=0.0 +y_0=0.0 +no_defs +units=km"))
```

Now, we created the spatial points dataframe and existing points are
Sterographic , and the units are in km

next, we transform it to lat/long

```{r, echo=FALSE}
lst_sp_fw_proj <- spTransform(lst_sp_fw, CRS("+proj=longlat +ellps=WGS84"))
```


Verify the bounding box
```{r, echo=FALSE}
summary(lst_sp_fw_proj)
bbox(lst_sp_fw_proj)
```

Lets try to plot it

```{r, echo=FALSE}
library(ggmap)
bgMap = get_map(as.vector(bbox(lst_sp_fw_proj)), source = "google", zoom = 3)
```

```{r, echo=FALSE}
plot(bgMap) 
```

Map is focusing on South America, means, transform didn't work
```{r, echo=FALSE}
# commemt

```
```{r, echo=FALSE}
# commemt

```
